---
title: "Assignment 1: Research Questions"
author: "Alicia Seeley, JT Keller, Alec Martinez"
date: "10/20/2021"
output: 
  html_document:
    theme: readable
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Research Question to Answer with Regression

Are people living in denser housing more likely to be civically and socially active?

# Prior Research

Citations for two research articles that address a question related to the one you’ve identified

### Potential Articles

#### The Impact of Public Housing on Social Networks: A Natural Experiment
https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2014.301949

#### Shaping for Civic Life: Can Better Design Help Engage Citizens?
https://archive.curbed.com/2017/6/22/15854608/urban-planning-community-engagement-litter

#### The Effect of Cohousing Model on People's Health and Wellbeing: A Scoping Review
https://publichealthreviews.biomedcentral.com/articles/10.1186/s40985-020-00138-1



# Sample Population and Variables

Our sample population includes adults in the US who participated in the IPUMS community civic engagement survey in November 2013.

## Categorial Variables

### 1. Living in Public Housing

#### whether or not the individual lives in public housing

### 2. Participated in a service or civic organization

#### whether or not the individual has participated in the last 12 months)

### 4. Group Quarters Type

## Continuous Variables

### 1. Units in Structure

#### number of units in individual's housing structure

### 2. Frequency of doing favors for neighbors and vice versa

### 3. Frequency of talking to neighbors




# Data Import

## Load Libraries

```{r, message=FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
library(ipumsr)
```


## Read in .dat file from IPUMS

```{r, message=FALSE, warning=FALSE}
ddi <- read_ipums_ddi("cps_00001.xml")
data <- read_ipums_micro(ddi)
```

## Read in .csv file

```{r}
civic <- read_csv("cps_00002.csv.gz")
```