---
title: "Assignment 1: Research Questions"
author: "Alicia Seeley, JT Keller, Alec Martinez"
date: "10/20/2021"
output: 
  html_document:
    theme: readable
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Research Question to Answer with Regression

How, if at all, is housing tenure and structure related to neighborhood social ties?

# Prior Research

We have identified two studies that show a positive relationship between housing tenure and different measures of social engagement. Levitten-Reid and Matthew (2018), using a sample from Canada, find "a positive association between home ownership and forms of bonding social capital". Similarly, Werner and Klingborg (2010), in a study conducted of Stockholm, Sweden, found results indicating that "residents forming tenant-owners associations have more trust in neighbors in the neighborhood."


# Sample Population and Variables

Our sample population includes adults in the US who participated in the IPUMS community civic engagement survey in November 2013.

## Categorial Variables

### 1. Housing Tenure

### 2. Participated in a service or civic organization

### 3. Trust in People in Neighborhood

## Continuous Variables

### 1. Units in Structure

#### number of units in individual's housing structure

### 2. Frequency of doing favors for neighbors and vice versa

### 3. Frequency of talking to neighbors





# Data Import

## Load Libraries

```{r, message=FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
library(ipumsr)
```


## Read in .dat file from IPUMS

```{r, message=FALSE, warning=FALSE}
ddi <- read_ipums_ddi("cps_00001.xml")
data <- read_ipums_micro(ddi)
```

## Read in .csv file

```{r}
civic <- read_csv("cps_00002.csv.gz")
```


```{r}
kable(head(data))
```

# References

Werner, Inga Britt, and Kerstin Klingborg. "Studying Social Capital In Housing Neighborhoods-Does Tenure Matter?." (2010).

Leviten-Reid, Catherine, and Rebecca A. Matthew. "Housing tenure and neighbourhood social capital." Housing, Theory and Society 35, no. 3 (2018): 300-328.

Sarah Flood, Miriam King, Renae Rodgers, Steven Ruggles, J. Robert Warren and Michael Westberry. Integrated Public Use Microdata Series, Current Population Survey: Version 9.0 [dataset]. Minneapolis, MN: IPUMS, 2021. https://doi.org/10.18128/D030.V9.0
